Placeholder Title... Something About Delegating Quantum Computations

### 2019-11-21 preliminaries.tex
Add QPIP

We define $\SampBQP$ the same way as from \cite{aaronson_2013}.

@@

\begin{definition}
	$\SampBQP$ is the class of sampling problems $S=(D_x)$ for which there exists a polynomial-time quantum algorithm that, given $x$ as input, samples from from a probability distribution $C_x$ such that $\norm{C_x-D_x}<\varepsilon$.
\end{definition}

>>>>

We define $\SampBQP$ based on \cite{aaronson_2013}.

@@

\begin{definition}
	$\SampBQP$ is the class of sampling problems $S=(D_x)$ for which for all $\varepsilon$ there exists a quantum circuit constructible in time $\poly(n, \frac{1}{\varepsilon})$ that, given $x$ as input, samples from from a probability distribution $\tilde{D}_x$ such that $\norm{\tilde{D}_x-D_x}<\varepsilon$.
\end{definition}

We then define a model of interation between a classical client and a quantum server. This is taken from \cite{mahadev_delegation}.

\begin{definition}
	A sampling problem $S=(D_x)$ is said to have a Quantum Prover Interactive Proof ($\QPIP$) with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
	\begin{itemize}
		\item $\bbP$ is a $\BQP$ machine.
		\item $\bbV$ is a $\BPP$ machine.
		\item There is a classical communication channel between $\bbP$ and $\bbV$.
		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$'s outputs has distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
	\end{itemize}
\end{definition}
